### 2018-06-15 express2018/unique.tex
Fixes in lemma 3.9 \ref{l:uptocon}

\begin{lemma}
\label{l:uptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\wb$
 of a system of weakly-guarded
contractions that uses  weakly-guarded sums.
For any context $\qct$ that uses  weakly-guarded sums, 
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a  context $\qctp$ that uses  weakly-guarded sums
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}

>>>>

\begin{lemma}
\label{l:uptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\mcontrBIS$
 of a system of weakly-guarded contractions (no direct sums).
For any context $\qct$ (no direct sums),
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a context $\qctp$ (no direct sums)
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arcap{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}
